\documentclass[12pt,fleqn]{article} 
\usepackage[margin=0.8in%, head=0.8in
]{geometry} 
\usepackage{amsmath, amssymb, amsthm}
\usepackage{fancyhdr} 
\usepackage{palatino, url, multicol}
\usepackage{graphicx} 
\usepackage[all]{xy}
\usepackage{polynom} 
\usepackage{pdfsync}
\usepackage{enumerate}
\usepackage{framed}
\usepackage{setspace}
\usepackage{array,tikz}
\pagestyle{fancy} 
%\usepackage{fancyhdr}
%\pagestyle{fancy}

\lhead{Math F113X: Numbers and Society}

\lfoot{UAF Math F113X}
\rfoot{first day }

\begin{document}
%\renewcommand{\headrulewidth}{0pt}
\newcommand{\blank}[1]{\rule{#1}{0.75pt}}
\renewcommand{\d}{\displaystyle}
%\vspace*{-0.7in}
\begin{center}
  \large \sc{First Day of Class Activity -- Some Solutions}
\end{center}


\begin{enumerate}
\item What is my teacher's name, office location, and email address?\\

This depends on your section.\\

\item Exchange \textbf{names} and \textbf{something memorable} with at least three people in the class. \\

This depends on your group. \\

Example: Jill Faudree moved to Fairbanks from Atlanta, Georgia without so much as a proper winter coat. \\

\item Where can I get information about this class?\\

The public webpage.\\
The Canvas course.\\
Your teacher and other members of the class.\\

\item Where is my textbook?\\

Free online. See links in Canvas and/or webpage.\\

\item How is my grade determined in this course? \\

Class participation, homework, miniquizzes, 3 midterms, final project.\\

\item Is there any extra credit or any free points in this class?\\

There is typically extra credit on all three midterms. There are lots of free points including: participation, homework, quiz corrections and midterm corrections.\\

\item What, if anything, is due \textbf{this} week in this class? \\

Your written answers to this activity need to be uploaded to Gradescope by Wednesday.\\

\item What if anything, is due \textbf{next} week in this class? \\

Homework 1 is due NEXT Wednesday. It will be followed by a miniquiz NEXT Friday over similar problems. \\

\item What should I do if I miss class?\\

Contact your instructor, explain the reason for your absence. Request information about what you need to do in order to keep up and not be completely lost the next class. \\

\item What should I do if I miss class on a quiz/midterm day?\\

Contact your instructor, explain the reason for your absence. Request to make-up the assignment. Keep in mind that it never hurts to ask but most classes have some kind of formal make-up policy for quizzes and/or midterms. \\

\item Is the homework completed in an online system or do I write it down? Where do I find the homework problems? How do I turn in the homework?\\

The homework is written - on paper or a tablet. The problems can be found at the Course Webpage under the \textbf{Homework} tab. You turn it in electronically using Gradescope which you access from Canvas.\\

\item Will I have answers or solutions to the homework? If so, where do I find them?\\

Yes. Complete solutions are on Canvas. They appear on the homepage and the \emph{Assessments} tab.\\


\item Can I just copy the solutions, upload them to Canvas and get full credit? \\

Yes. \\
It should be clear that this is a very bad long-term strategy.\\

\item Can I see my grades?\\

Grades live in Canvas.\\

\item How can I get my questions answered?\\

in class\\
instructor's office hours\\
Send your instructor an email\\
in the Math \& Stat tutoring lab (drop in or by appointment)\\
textbook and/or associated videos\\
your classmates\\

\item Where can I get tutoring help?\\

Math \& Stat Lab on the same floor as this classroom.\\

\item How will my teacher contact me? \\

In class. Canvas. Email sent to your UAF email address.\\


\item What are the habits I would like to adopt this semester in this class?\\

Obviously, there are no wrong answers here.  However, it is worth pointing out that certain habits have been shown to increase learning and/or raise the chances of passing a college course. These include:

\begin{itemize}
\item Attending class every day.
\item Participating in class activities.
\item Knowing one other person in the class by name.
\item Starting the assignments early and turning them in on time.
\item Having set times and locations during the week for completing the class assignments.
\item Keeping track of your questions and having a set time each week for getting them answered.
\item Visiting your teacher's office hours in the first two weeks of class and regularly after than.
\item Completing (and correcting) a practice assessment prior to taking the one that counts.
\end{itemize}
\end{enumerate}
\end{document}