\documentclass[12pt]{article}

% Layout.
\usepackage[top=1in, bottom=0.75in, left=1in, right=1in, headheight=1in, headsep=6pt]{geometry}

% Fonts.
\usepackage{mathptmx}
\usepackage[scaled=0.86]{helvet}
\renewcommand{\emph}[1]{\textsf{\textbf{#1}}}

% TiKZ.
\usepackage{tikz, pgfplots,xcolor}

\usetikzlibrary{calc,trees,positioning,arrows,fit,shapes,through, backgrounds}
\usetikzlibrary{patterns}

\usetikzlibrary{decorations.markings}
\usetikzlibrary{arrows}

\usepackage{pgfplots}


% Misc packages.
\usepackage{amsmath,amssymb,latexsym}
\usepackage{graphicx}
\usepackage{array}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{fancyhdr}
\pagestyle{fancy}


% Misc.
\renewcommand{\d}{\displaystyle}
\newcommand{\ds}{\displaystyle}
\newcommand{\ul}[1]{\underline{#1}}
\def\bc{\begin{center}}
\def\ec{\end{center}}
\def\be{\begin{enumerate}}
\def\ee{\end{enumerate}}

\newcommand{\ans}[1][1in]{\rule{#1}{.5pt}}


\lhead{Math F113X: Quiz 8}
\rhead{April 18, 2025}

\begin{document}

\vspace{1cm}
\strut

\noindent \textbf{Name:} \hrulefill \quad  score:\ans[1cm] \ / 10 \\


\noindent There (really) are 10 points possible on this quiz. No aids (book, notes, etc.)
are permitted. You may use a calculator.  {\bf Show all work and supporting calculations for full credit. Explain how you get your answers.}

A tabula recta is available.
\be

\item (2 points)  \textbf{Encrypt} the message SUMMER TIME using a tabular transposition cipher with the encryption key word ``BREAK."

\vfill

\item (2 points)  \textbf{Decrypt} the message  below assuming it was encrypted using a tabular transposition cipher with the encryption key word ``BREAK."

$$F\:N\:L\:N\:I\:\:\quad C\:T\:A\:I\:L\:\:\quad D\:L\:E\:X\:H$$

%% NETFLIX AND CHILL

\vfill
\newpage

%\item (2 points)  \textbf{Encrypt} the message ALMOST DONE using a shifting Caesar cipher that starts with a shift of 4 (mapping A to E).\\
%\vfill

\item (3 points) \textbf{Decrypt} the message below assuming it was encrypted using a Vigen\`{e}re cipher with encryption key word ``SUN."

$$K\:C\:K\:E\:\quad I\:E\:W\:J \:\quad R\:J\:X\:N \:\quad Q$$

%%six more per day

\vfill


\item (1 point)  Compare a Vigen\`{e}re cipher to a tabular transposition cipher. What are the advantages and/or disadvantages.
\vfill
\item (2 points) Your bill at a restaurant is \$34.78 and you want to leave an 18\% tip. How much would you add to the bill? (Show both your computation and your answer.)
\vfill
\ee
\end{document}