\documentclass[11pt, oneside]{article}   	
\usepackage{geometry}                		
\geometry{letterpaper}                   		
\usepackage[parfill]{parskip}    		
\usepackage{graphicx}						
\usepackage{amssymb, enumerate}

%begin document
\begin{document}
\begin{center} {\Large{MATH F113X: Homework 2}} \end{center}
\vspace{.3in}

\fbox{\parbox{\textwidth}{
\begin{itemize}
\item Answer the following problems from the Voting Theory section (p.53):
\begin{quote}\# 3def, 6def, 12, 13-16, 18, 24ab, Problem A\end{quote}
\item Answer the following problems from the Weighted Voting  section (p.70):
\begin{quote}\# 2, 4, 5, 6, 10 \end{quote}
\end{itemize}
}}

{\bf Problem A:}
\begin{enumerate}[(1)]
\item Explain Arrow's Impossibility Theorem in your own words in such a way that a typical adult could understand it. 

\item The President of the United States is elected by the Electoral College. Now that you have learned a lot about voting schemes, what scheme would \textbf{you} choose to elect the President of the United States and why? (A short paragraph is sufficient even though we all know entire books can be written on this topic!)

\item How has learning about voting schemes changed your view of voting and elections? \end{enumerate}
\vfill
Remember to write up your homework solutions according to the homework writeup guidelines. Confirm your work is correct or fix your errors before you submit it. Homework must be submitted on Gradescope. \\
\vfill
\textbf{Rubric:}

\begin{description}
\item[2 points:] You provided a complete answer, with supporting work, written up clearly
\item[1 point:] Some attempt at a solution, but incomplete writeup / unclear / illegible / no answer
\item[1 point:] Only an answer, with no supporting work 
\item[0 points:] Missing.
\end{description}



\end{document}  