% !TEX TS-program = pdflatexmk
\documentclass[12pt]{article}

% Layout.
\usepackage[top=1in, bottom=0.75in, left=1in, right=1in, headheight=1in, headsep=6pt]{geometry}

% Fonts.
\usepackage{mathptmx}
\usepackage[scaled=0.86]{helvet}
\renewcommand{\emph}[1]{\textsf{\textbf{#1}}}

% Misc packages.
\usepackage{amsmath,amssymb,latexsym}
\usepackage{graphicx,hyperref}
\usepackage{array}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{tabularx,colortbl,booktabs,xparse}
\usepackage{enumitem}

% Rotation: \rot[<angle>][<width>]{<stuff>}
\NewDocumentCommand{\rot}{O{45} O{1em} m}{\makebox[#2][l]{\rotatebox{#1}{#3}}}%

\usepackage{fancyhdr}
\pagestyle{fancy} 
\lhead{\large\sf\textbf{MATH F113X: Weighted Voting}}
\chead{\large\sf\textbf{lecture notes}}
\rhead{\large\sf\textbf{Banzaf Power Index}}

\begin{document}
\begin{center} Review \end{center}
\begin{enumerate}
\item Answer questions about the weighted voting system below.
$$[67: 50,30,10,5,4,1].$$
	\begin{enumerate}
	\item How many players are there? \underline{\hspace{.5in}}\\
	\item What is the quota? \underline{\hspace{.5in}}\\
	\item What is the total weight of the voting system? \underline{\hspace{.5in}}\\
	\end{enumerate}
\item Explain the terminology below. Then use the voting system from \#1 to add illuminating examples.
	\begin{enumerate}
	\item coalition
	\vfill
	\item winning coalition
	\vfill
	\item critical player
	\vfill
	\item dictator
	\vfill
	\item a player with veto power
	\vfill
	\item a dummy player
	\vfill
	\end{enumerate}
\newpage
\item Answer questions about the weighted voting system below.
$$[30: 25, 10, 5]$$
	\begin{enumerate}
	\item List \emph{ALL} coalitions.
	\vfill
	\item List all \emph{WINNING} coalitions.
	\vfill
	\item In each \emph{winning} coalition listed above, underline the critical players.\\	
	\item Calculate the Banzhaf Power index.
\begin{enumerate}
\item Find all winning coalitions
\item Find all critical players
\item Underline critical players
\item Count total \# underlines
\item For each player, compute:
\end{enumerate}

	
	\vspace{3in}
	\end{enumerate}
	

\end{enumerate}
\end{document}