\documentclass[12pt,fleqn]{article} 
\usepackage[margin=0.8in%, head=0.8in
]{geometry} 
\usepackage{amsmath, amssymb, amsthm}
\usepackage{fancyhdr} 
\usepackage{palatino, url, multicol}
\usepackage{graphicx} 
\usepackage[all]{xy}
\usepackage{polynom} 
\usepackage{pdfsync}
\usepackage{enumerate}
\usepackage{framed}
\usepackage{setspace}
\usepackage{array,tikz}
\pagestyle{fancy} 
%\usepackage{fancyhdr}
%\pagestyle{fancy}

\lhead{Math F113X: Numbers and Society}

\lfoot{UAF Math F113X}
\rfoot{first day }

\begin{document}
%\renewcommand{\headrulewidth}{0pt}
\newcommand{\blank}[1]{\rule{#1}{0.75pt}}
\renewcommand{\d}{\displaystyle}
%\vspace*{-0.7in}
\begin{center}
  \large \sc{First Day of Class Activity}
\end{center}


\begin{enumerate}
\item What is my teacher's name, office location, and email address?

\vfill

\item Exchange \textbf{names} and \textbf{something memorable} with at least three people in the class. 
\vspace{2in}

\item Where can I get information about this class?\\


\vfill
\item Where is my textbook?\\

\vfill
\item How is my grade determined in this course? \\

\vfill
\item Is there any extra credit or any free points in this class?\\

\vfill
\item What, if anything, is due \textbf{this} week in this class? \\
\vfill
\item What if anything, is due \textbf{next} week in this class? \\
\vfill
\newpage
\item What should I do if I miss class?

\vfill

\item What should I do if I miss class on a quiz/midterm day?

\vfill

\item Is the homework completed in an online system or do I write it down? Where do I find the homework problems? How do I turn in the homework?
%The homework is written. The problems can be found at the Course Webpage. You turn it in electronically using Gradescope which you access from Canvas.
\vfill
\item Will I have answers or solutions to the homework? If so, where do I find them?\\
%Yes. Complete solutions are on Canvas. Look in the \emph{Assessments} tab.
\vfill
\item Can I just copy the solutions, upload them to Canvas and get full credit? \\
%Yes. 
%It should be clear that this is a very bad long-term strategy. See the answer to question \#8.
\vfill
\item Can I see my grades?\\
%Grades live in Canvas.
\vfill

\item What is the best way to get my questions answered?\\

\vfill

\item Where can I get tutoring help?\\
%Chapman 305, upstairs. Notably on the same floor as Jill's office. Note that Jill and our TA's have weekly hours in the math lab!
\vfill
\item How will my teacher contact me? \\
%In class. Canvas. Email.
\vfill

\item What are the habits \emph{you} would like to adopt this semester in this class?
\vfill
\end{enumerate}
\end{document}