% !TEX TS-program = pdflatexmk
\documentclass[12pt]{article}

% Layout.
\usepackage[top=1in, bottom=0.75in, left=1in, right=1in, headheight=1in, headsep=6pt]{geometry}

% Fonts.
\usepackage{mathptmx}
\usepackage[scaled=0.86]{helvet}
\renewcommand{\emph}[1]{\textsf{\textbf{#1}}}

% Misc packages.
\usepackage{amsmath,amssymb,latexsym}
\usepackage{graphicx,hyperref}
\usepackage{array}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{tabularx,colortbl,booktabs,xparse}
\usepackage{enumitem}

% Rotation: \rot[<angle>][<width>]{<stuff>}
\NewDocumentCommand{\rot}{O{45} O{1em} m}{\makebox[#2][l]{\rotatebox{#1}{#3}}}%

\usepackage{fancyhdr}
\pagestyle{fancy} 
\lhead{\large\sf\textbf{MATH F113X: Weighted Voting}}
\chead{\large\sf\textbf{lecture notes}}
\rhead{\large\sf\textbf{Day 2}}

\begin{document}
Goal: Understand how the Banzhaf Power Index is Calculated 
\begin{enumerate}
\item \textbf{Review}: Answer questions about the weighted voting system below.
$$[67: 50,30,10,5,4,1].$$
	\begin{enumerate}
	\item How many players are there? \underline{\hspace{.5in}}\\
	\item What is the quota? \underline{\hspace{.5in}}\\
	\item What is the total vote? \underline{\hspace{.5in}}\\
	\item Is there a dictator? Explain.\\
	\vfill
	\item Does any player have veto power? If so, find them and \emph{justify} your conclusion.\\
	\vfill
	\item Are there any dummy players? If so, find them and \emph{justify} your conclusion.\\
	\vfill
	\end{enumerate}
\item Recall:

\emph{ Coalition}

\vfill

\emph{  Winning Coalition}

\vfill

\emph{ Critical Player}

\vfill



\newpage
\item Answer questions about the weighted voting system below.
$$[30: 25, 10, 5]$$
	\begin{enumerate}
	\item List \emph{ALL} coalitions.
	\vfill
	\item List all \emph{WINNING} coalitions.
	\vfill
	\item In each \emph{winning} coalition, identify which players are critical.
	\vfill
	\item Calculate the Banzhaf Power index.
\begin{enumerate}
\item Find all winning coalitions
\item Find all critical players
\item Underline critical players
\item Count total \# underlines
\item For each player, compute:
\end{enumerate}

	
	\vfill
	\end{enumerate}
	

\end{enumerate}
\end{document}