% !TEX TS-program = pdflatexmk
\documentclass[12pt]{article}

% Layout.
\usepackage[top=1in, bottom=0.75in, left=1in, right=1in, headheight=1in, headsep=6pt]{geometry}

% Fonts.
\usepackage{mathptmx}
\usepackage[scaled=0.86]{helvet}
\renewcommand{\emph}[1]{\textsf{\textbf{#1}}}

% Misc packages.
\usepackage{amsmath,amssymb,latexsym}
\usepackage{graphicx,hyperref}
\usepackage{array}
\usepackage{xcolor}
\usepackage{multicol,tikz}
\usepackage{tabularx,colortbl,booktabs,xparse}
\usepackage{enumitem}

% Rotation: \rot[<angle>][<width>]{<stuff>}
\NewDocumentCommand{\rot}{O{45} O{1em} m}{\makebox[#2][l]{\rotatebox{#1}{#3}}}%

\usepackage{fancyhdr}
\pagestyle{fancy} 
\lhead{\large\sf\textbf{MATH F113X: Fair Division}}
\chead{\large\sf\textbf{lecture notes}}
\rhead{\large\sf\textbf{Day 2}}

\begin{document}
Goal: Review Divider-Chooser, Introduce Lone-Divider
\begin{enumerate}
\item Recall from the previous worksheet: \quad Tom and Fred were given a cake worth \$12 that is equal parts strawberry, vanilla and chocolate, their respective values summarized in the chart.\\
\begin{multicols}{2}
%table
\begin{tabular}{c||ccc}
&vanilla&strawberry&chocolate\\
\hline \hline
Tom&\$ 6 & \$ 6 & \$ 0\\
Fred&\$ 2&\$ 4 & \$ 6
\end{tabular}
%figure
\begin{tikzpicture}[scale = .6]
\def\r{2}
\draw (0,0) circle (\r cm);
\filldraw[fill= gray!20 ] (0,0) -- (0:\r) arc (0:120:\r) -- (0,0);
\path (60:1) node[]{{{\scriptsize Strawberry}}};
%\path node[right] (240:1) {{\scriptsize Strawberry}};
\filldraw[fill = gray!60 ] (0,0) -- (120:\r) arc (120:240:\r) -- (0,0);
\path (120+60:\r/2) node[]{{{\scriptsize Chocolate}}};
\path (-60:\r/2) node[]{{{\scriptsize Vanilla}}};
\end{tikzpicture}
\end{multicols}
	\begin{enumerate}
	\item Divide the cake using Divider-Choose assuming Tom is the divider. Determine the \emph{value} of the assigned share to each party.\\
\begin{tikzpicture}[scale = .8]
\def\r{2}
\draw (0,0) circle (\r cm);
\filldraw[fill= gray!20 ] (0,0) -- (0:\r) arc (0:120:\r) -- (0,0);
\path (60:1) node[]{{{\scriptsize Strawberry}}};
%\path node[right] (240:1) {{\scriptsize Strawberry}};
\filldraw[fill = gray!60 ] (0,0) -- (120:\r) arc (120:240:\r) -- (0,0);
\path (120+60:\r/2) node[]{{{\scriptsize Chocolate}}};
\path (-60:\r/2) node[]{{{\scriptsize Vanilla}}};
\end{tikzpicture}
\vfill	
	\item Divide the cake using Divider-Choose assuming Fred is the divider. Determine the \emph{value} of the assigned share to each party.\\
\\
\begin{tikzpicture}[scale = .8]
\def\r{2}
\draw (0,0) circle (\r cm);
\filldraw[fill= gray!20 ] (0,0) -- (0:\r) arc (0:120:\r) -- (0,0);
\path (60:1) node[]{{{\scriptsize Strawberry}}};
%\path node[right] (240:1) {{\scriptsize Strawberry}};
\filldraw[fill = gray!60 ] (0,0) -- (120:\r) arc (120:240:\r) -- (0,0);
\path (120+60:\r/2) node[]{{{\scriptsize Chocolate}}};
\path (-60:\r/2) node[]{{{\scriptsize Vanilla}}};
\end{tikzpicture}
	\end{enumerate}
\vfill
\item Is it better to be the Divider or the Chooser? Why?
\vspace{0.5in}
\newpage
\item Lone-Divider Method (for $N$ people with $N \geq 3$).
	\begin{enumerate}
	\item[0.] \emph{Arbitrarily} pick a Divider.
	\item[1.] The Divider divides the items into $N$ shares of equal value to them: $s_1,s_2, \cdots, s_N$.
	\item[2.] The remaining parties \textbf{declare} or \textbf{bid} on which the shares, $s_1,s_2, \cdots, s_N,$ they consider fair. 
	\item[3.] 
		\begin{enumerate}
		\item \textbf{IF} the $N$ shares can be divided among the parties such that each gets a fair share, then do so. 
		\item \textbf{IF NOT}, then give the Divider a \textbf{non-contested piece}. Then restart Lone-Divider with $N-1$ parties: recombine the shares and re-divide.
		\item Once you're down to 2 parties, use Divider-Chooser.
		\end{enumerate}
	\end{enumerate}
\item \textbf{Example 1} Suppose Patrick, Chris, and Travis are splitting a pile of football memorabilia estimated to be worth \$300. It has been split into 3 shares and their respective values are summarized in the table.

(a) What is a fair share? \rule{2cm}{.5pt}
\begin{multicols}{2}
\begin{tabular}{c||c|c|c}
&$s_1$&$s_2$&$s_3$\\
\hline \hline
Patrick&\$50&\$150&\$100\\
Chris&\$70&\$70&\$160\\
Travis&\$100&\$100&\$100\\
\end{tabular} 

(b) Circle or highlight each individual's \textbf{bid} (the shares they would consider to be fair).\\

(c) Determine which person was the Divider.
\end{multicols}
(d) Determine the next steps of the Lone-Divider Method.
\vfill
\item \textbf{Example 2} Suppose Patrick, Chris, and Travis are splitting a pile of football memorabilia estimated to be worth \$300. It has been split into 3 (different) shares and their respective values are summarized in the table.
\begin{multicols}{2}
\begin{tabular}{c||c|c|c}
&$t_1$&$t_2$&$t_3$\\
\hline \hline
Patrick&\$100&\$100&\$100\\
Chris&\$90&\$40&\$170\\
Travis&\$50&\$90&\$160\\
\end{tabular} 

(a) Circle or highlight each individual's \textbf{bid} (the shares they would consider to be fair).\\

(b) Determine which person was the Divider.
\end{multicols}
(c) Determine the next steps of the Lone-Divider Method.
\vfill

\end{enumerate}
\end{document}